### 2019-07-08 bp_studyMethod.tex
addressed concerns from Reviewer 1 using information from their review and our rebuttal

\begin{table}[h!]
\begin{center}
\begin{tabular}{l l}
\hline
Biometric Measurement & Units of Measure \\ 
\hline
\textbf{Physical Activity} & \cite{fox1999,aldana1996}\\
\hspace{3mm}Intensity of motion & (No unit)  \\
\hspace{3mm}Energy Expenditure & Calories per second (cal/s)  \\
\hspace{3mm}Step counter & Steps  \\
\hline
\textbf{Heart} & \cite{haapalainen2010psycho,healey2005detecting,mulder1992measurement,haag2004emotion} \\
\hspace{3mm}Heart rate & Beats per Minute (bpm) \\
\hspace{3mm}Blood pulse wave & (No Unit)  \\
\hspace{3mm}Heart rate variability & Milliseconds (ms) \\
\hspace{3mm}Blood oxygenation  & Percent (\%)  \\
\hspace{3mm}Blood perfusion & (No unit)  \\
\hline
\textbf{Skin} & \cite{healey2005detecting,haag2004emotion} \\
\hspace{3mm}Galvanic skin response &  kOhm  \\
\hspace{3mm}Skin temperature &  Degrees Celsius ($^{\circ}$C)  \\
\hline
\textbf{Respiration} & \cite{mulder1992measurement,healey2005detecting,haag2004emotion,masaoka1997}\\
\hspace{3mm}Respiratory rate & Breaths per Minute (bpm)  \\
\hline
%\textbf{Environmental}\\
%\hspace{3mm}Barometric pressure & Milibar (mbar)  \\
%\hline
\end{tabular}
\caption{Biometric measurements captured by the Everion, organized by category and with references to previous works using similar data}
\label{signals}
\end{center}
\vspace*{-4mm}
\end{table}

\subsubsection{Surveys}
\label{sec:Surveys}
We sent via text message a survey request to each participant two times per work day. We sent the first request at a random time between 9am and 11am and sent the second request at a random time between 1pm and 3pm. We randomized the request times to avoid either establishing or observing a standard behavioral pattern. That is, we did not want the participants to plan for the arrival of the survey request at a set time, and we did not want the survey request to overlap with a set daily behavior (e.g., coffee break every day at 2:30pm). The same survey was sent each time:
\begin{enumerate}
\item How awake are you right now?
\item How stressed do you feel right now?
\item How focused on work are you right now? 
\end{enumerate}
We used the phrase ``right now'' to capture each aspect in the moment (so as to permit later prediction of each aspect based on biometric data). The wordings of the questions are based on a previous survey of individuals in an organizational context~\cite{Gloor_etal:2010}. The use of awakeness (rather than sleepiness) in Question 1 is inspired by previous work~\cite{Wilhelm_Schoebi:2007} and to some extent also captures the ``arousal'' aspect of the affective space~\cite{Russell:1980}.

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{l l}
\hline
Biometric Measurement & Units of Measure \\ 
\hline
\textbf{Physical Activity} & \cite{fox1999,aldana1996}\\
\hspace{3mm}Intensity of motion & (No unit)  \\
\hspace{3mm}Energy Expenditure & Calories per second (cal/s)  \\
\hspace{3mm}Step counter & Steps  \\
\hline
\textbf{Heart} & \cite{haapalainen2010psycho,healey2005detecting,mulder1992measurement,haag2004emotion} \\
\hspace{3mm}Heart rate & Beats per Minute (bpm) \\
\hspace{3mm}Blood pulse wave & (No Unit)  \\
\hspace{3mm}Heart rate variability (RMSSD) & Milliseconds (ms) \\
\hspace{3mm}Blood oxygenation  & Percent (\%)  \\
\hspace{3mm}Blood perfusion & (No unit)  \\
\hline
\textbf{Skin} & \cite{healey2005detecting,haag2004emotion} \\
\hspace{3mm}Galvanic skin response &  kOhm  \\
\hspace{3mm}Skin temperature &  Degrees Celsius ($^{\circ}$C)  \\
\hline
\textbf{Respiration} & \cite{mulder1992measurement,healey2005detecting,haag2004emotion,masaoka1997}\\
\hspace{3mm}Respiratory rate & Breaths per Minute (bpm)  \\
\hline
%\textbf{Environmental}\\
%\hspace{3mm}Barometric pressure & Milibar (mbar)  \\
%\hline
\end{tabular}
\caption{Biometric measurements captured by the Everion, organized by category and with references to previous works using similar data}
\label{signals}
\end{center}
\vspace*{-4mm}
\end{table}

\subsubsection{Surveys}
\label{sec:Surveys}
Following guidelines from previous studies~\cite{Lalle16,Panwar18,Luo18} and 
following the preferrences of extensive user piloting, we sent via 
text message a survey request to each participant two times per 
work day. Pilot participants preferred these over other means, in part, due 
to them being accessible and noticeable anywhere in the office.

We sent the 
first request at a random time between 9am and 11am 
and sent the second request at a random time between 1pm and 3pm. We 
randomized the request times to avoid either establishing or observing a 
standard behavioral pattern. That is, we did not want the participants to 
plan for the arrival of the survey request at a set time, and we did not 
want the survey request to overlap with a set daily behavior (e.g., coffee 
break every day at 2:30pm). Similarly, we avoided using tools which allow 
for too much freedom in response time~\cite{Adams18} since this would 
discurage participation in stressed timeframes and would bias the 
corpus. 
%This sentence was added in response to Reviewer 1 comment:
%There is already a lot of work on designing a new self-log, a self-report 
%tool which can blend into the workstation [1] or offers users more freedom 
%in time to self-report [2], or facilitate the self-log by using wearables.
The same survey was sent each time:
\begin{enumerate}
\item How awake are you right now?
\item How stressed do you feel right now?
\item How focused on work are you right now? 
\end{enumerate}
We used the phrase ``right now'' to capture each aspect in the moment (so as to permit later prediction of each aspect based on biometric data). The wordings of the questions are based on a previous survey of individuals in an organizational context~\cite{Gloor_etal:2010}. The use of awakeness (rather than sleepiness) in Question 1 is inspired by previous work~\cite{Wilhelm_Schoebi:2007} and to some extent also captures the ``arousal'' aspect of the affective space~\cite{Russell:1980}.
